\documentclass[
  %solution,
  english
	%german
]{tumteaching}

\usepackage{listings}
\usepackage{paralist}

\usepackage{mathpartir}
\usepackage{stmaryrd}
\usepackage{braket}
\usepackage[inline]{enumitem}
\usepackage{amsmath,amsthm}
\usepackage{multirow}
\usepackage{url}
\usepackage[dvipsnames]{xcolor}
\usepackage{centernot}
\usepackage{multicol}
\usepackage{adjustbox}
\usepackage{ltablex}
\usepackage{comment}

\usepackage{info2}

\usetikzlibrary{decorations.pathmorphing}
\usetikzlibrary{shapes.callouts}

\tikzset{snake it/.style={decorate, decoration=snake}}

\ExplSyntaxOn%
\tl_gset:Nn \g_tumteaching_date_tl {WS~2018/19}
\tl_gset:Nn \g_tumteaching_exsheet_nr_tl {4}
\tl_gset:Nn \g_tumteaching_exsheet_deadline_tl {18.11.2018}
\ExplSyntaxOff%

\newcommand{\objective}[1]{\item \small{#1}}
%\newcommand{\mydottedline}[0]{...}
\newcommand{\mydotline}{\makebox[2.0in]{\dotfill}}
\newcolumntype{C}{>{\centering\arraybackslash}X}


\begin{document}

\verticalline
\begin{disclaimer}{General Information}
	Detailed information about the lecture, tutorials and homework assignments can be found on the lecture website\footnote{\url{https://www.in.tum.de/i02/lehre/wintersemester-1819/vorlesungen/functional-programming-and-verification/}}. Solutions have to be submitted to Moodle\footnote{\url{https://www.moodle.tum.de/course/view.php?id=44932}}. Make sure your uploaded documents are readable. Blurred images will be rejected. Use Piazza\footnote{\url{https://piazza.com/tum.de/fall2018/in0003/home}} to ask questions and discuss with your fellow students.
\end{disclaimer}

\verticalline
\vspace*{-5mm}

\begin{disclaimer}{Simplifications}
	Make sure you simplify terms whenever possible. Overly complex proofs with huge formulas due to lack of any meaningful simplification will not be awarded with full points.
\end{disclaimer}

\verticalline
\vspace*{-5mm}

\begin{disclaimer}{OCaml Setup}
	We are going to start OCaml programming in next week's exercises. Please prepare your machines accordingly and bring them to the sessions. A detailed installation guide will be published soon. Please check the website and Moodle.
\end{disclaimer}

\verticalline

\begin{assignment}[L]{Termination}
In the lecture, you have learned how to prove termination of a MiniJava program. Discuss these questions:
	\begin{enumerate}
		\item How can you decide whether a termination proof is required at all?
		\item What is the basic idea of the termination proof?
		\item How has the program to be modified?
		\item What has to be proven?
		\item How is the loop invariant influenced?
	\end{enumerate}		

	
\end{assignment}

\clearpage
\begin{assignment}[L]{Counter Time}
	Prove that the following program does indeed terminate for all inputs.
	\begin{center}
		\begin{tikzpicture}
			\input{cfg3.c.cfg.tex}
		\end{tikzpicture}
	\end{center}

	\clearpage
\end{assignment}

\clearpage
\begin{assignment}[L]{A Wavy Approach}
	Prove termination of the following program:
	\begin{center}
		\begin{tikzpicture}
			\input{cfg1.c.cfg.tex}
		\end{tikzpicture}
	\end{center}

\end{assignment}

\clearpage
\begin{assignment}[H,points=6]{Counting Twelves}
	Prove termination of the following program:
	\begin{center}
		\begin{tikzpicture}
			\input{cfg5.c.cfg.tex}
		\end{tikzpicture}
	\end{center}

\end{assignment}

\clearpage
\begin{assignment}[H,points=4]{aaaaaaaaaab}
	Prove termination of the following program:
	\begin{center}
		\begin{tikzpicture}
			\input{cfg6.c.cfg.tex}
		\end{tikzpicture}
	\end{center}

\end{assignment}

\clearpage
\begin{assignment}[H,points=10]{Term-ination}
	Prove that the following program terminates for all inputs:
	\begin{center}
		\begin{tikzpicture}
			\input{cfg4.c.cfg.tex}
		\end{tikzpicture}
	\end{center}

	\noindent\hint{Finding a formula for $r$ is non-trivial in this program. Make sure you understand what the program is doing and consider writing down the values of variables for a couple of iterations.}
	
	\noindent\hint{Keep in mind, that $r$ need not necessarily represent the exact number of remaining loop iterations, but a finite upper limit.}

\end{assignment}

\begin{comment}
\begin{assignment}[H,points=8]{Name}
TODO: fix, this does not terminate for negative n
	\begin{center}
		\begin{tikzpicture}
			\input{cfg2.c.cfg.tex}
		\end{tikzpicture}
	\end{center}
\end{assignment}
\end{comment}

\end{document}





































